---
title: "2nd-Assignment-Soln"
author: "Ketan Bhadoriya"
output: html_document
---

#Data analysis and visualization in R- Using ggplot2

###Loading required packages

```{r,warning=FALSE}
library(ggplot2)
```

###Loading the Data

```{r}
movie.hw <- read.csv("Section6-Homework-Data.csv")
```

###Exploring the Data

```{r}
head(movie.hw)

tail(movie.hw)

str(movie.hw)

colnames(movie.hw)

summary(movie.hw)

levels(movie.hw$Genre)

levels(movie.hw$Studio)
```

###Research Question

We are interested in finding the Domestic Gross % by Genre and Studio and size the graph based on Budget.

Note : Since there are a lot of Genre and Studios we will be looking at only a few

```{r,warning=FALSE}
#Filter for Genre
filter1 <- (movie.hw$Genre == "action") | (movie.hw$Genre == "adventure") |
  (movie.hw$Genre == "animation") | (movie.hw$Genre == "comedy") |
  (movie.hw$Genre == "drama")

#Filter for Studio
filter2 <- (movie.hw$Studio == "Buena Vista Studios") | (movie.hw$Studio == "WB") |
  (movie.hw$Studio == "Fox") | (movie.hw$Studio == "Universal") | (movie.hw$Studio=="Sony")|
  (movie.hw$Studio == "Paramount Pictures")

#New DataFrame
movie.hw2 <- movie.hw[filter1 & filter2,]

head(movie.hw2)

#Visualizing the Data

d <- ggplot(data=movie.hw2,aes(x=Genre,y=Gross...US))

f <- d +geom_jitter(aes(size= Budget...mill.,color=Studio)) + 
  geom_boxplot(alpha=0.6, outlier.colour = NA)

final <- f + xlab("Genre") +
             ylab("Gross % US") +
             ggtitle("Domestic Gross % by Genre") +
             theme(text = element_text(family = "Comic Sans MS"),
             axis.title = element_text(color = "Blue"),
             plot.title = element_text(size = 20))

final$labels$size = "Budget in Millions(US $)"

final
```

###Conclusion

* Comedy has the highest Gross % in US and Adventure the least
* Drama has the least variation
* Most movies made are Action

####Reference

>Please note that the above datasets, and research question has been obtained from [www.superdatascience.com](https://www.superdatascience.com/), obtained while pursuing a course by Kirill Eremenko